The function--sheaf dictionary for smooth commutative group schemes over finite fields, with applications over local fields

### 2014-08-22 dictionary.tex
Changes to the first half of the Introduction.

Motivated by an application to the geometrization and categorification of quasicharacters of $p$-adic tori,
this paper extends Deligne's function--sheaf dictionary for connected commutative algebraic groups over finite fields to all smooth commutative group schemes over finite fields.

@@

In order to extend the dictionary from commutative algebraic groups over finite fields to smooth commutative group schemes $G$ over $\FF_q$ we simply replace the local system $\qcs{E}$ on $G$ with a Weil local system, while retaining the extra structure $\mu_\qcs{E}$.
In this way we are lead to the category $\QC(G)$ of {\it quasicharacter sheaves} on $G$ in which objects are triples $(\gqcs{L}, \mu,\phi)$, where $\gqcs{L}$ is a rank-one local system on ${\bar G} = G\times_{\Spec{\FF_q}} \Spec{{\bar \FF}_q}$ and $\phi : \Frob{G}^* \gqcs{L}\to \gqcs{L}$ and $\mu : {\bar m}^* \gqcs{L} \iso \gqcs{L} \boxtimes \gqcs{L}$ are isomorphisms of sheaves; the isomorphisms $\mu$ and $\phi$ must of course be compatible in the obvious way. Morphism in $\QC(G)$ are then homomorphisms of Weil sheaves which are compatible with the extra structure.

We first test the category of quasicharacter sheaves by examining its objects on étale commutative group schemes $G$ over $\FF_q$; étale group schemes form a counterpoint to connected algebraic groups, since the component group of a smooth commutative group scheme is an étale group scheme. 
We find that the group homomorphism 
\begin{equation}
T_G: \QCiso{G} \to \Hom(G(\FF_q),\EEx)
\end{equation}
provided by the trace of Frobenius is surjective with kernel $\Hh^2(\bG,\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$, canonically.
One can show, using the Kunneth formula, that $\Hh^2(\bG,\EEx)$ is non-trivial unless $\bG$ is cyclic.
The fact that $T_G$ is not an isomorphism should not be too troubling because if quasicharacter sheaves $(\gqcs{L}, \mu,\phi)$ and $(\gqcs{L}', \mu',\phi')$ determine the same character of $G(\FF_q)$ then $(\gqcs{L},\phi)$ and $(\gqcs{L}',\phi')$ are isomorphic as Weil sheaves.
Here we also see the importance of working with Weil sheaves: without them, we would not be able to geometrize the character of the étale group scheme $\ZZ$ over $\FF_q$ given by $1\mapsto \ell$, for example.

@@

Having understood quasicharacter sheaves on commutative smooth group schemes over $\FF_q$ in two extreme cases -- connected algebraic groups and étale commutative group schemes -- we turn to the general case. Remarkably, we find that the general case can be understood from these two extreme cases, using the component group sequence
\begin{equation}
0 \to G^0 \to G \to \pi_0(G) \to 0.
\end{equation}
The main result of the paper uses this sequence to find $\QCiso{G}$ by situating it in a canonical short exact sequence
\begin{equation}
0 \to \Hh^2(\pi_0(\bG),\EEx)^{\Gal({\bar\FF}_q/\FF_q)} \to \QCiso{G} \to \Hom(G(\FF_q),\EEx) \to 0.
\end{equation}
We remark that $\Hh^2(\pi_0(\bG),\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$ is non-trivial even for some commutative algebraic groups.
We also illuminate the nature of the category $\QC(G)$ by showing that every morphism in this category is either an isomorphism or trivial, and by showing that 
\begin{equation}
\Aut(\qcs{L}) \iso \Hom(\pi_0(\bG)_{\Gal(\bFq/\Fq)},\EEx),
\end{equation}
canonically, for all quasicharacter sheaves $\qcs{L}$ on $G$.

@@

Specializing to the case when $X_K$ is an algebraic tori $T$ over $K$, and writing $\underline{T}$ for the Neron model $X$ in this case, this paper gives a canonical short exact sequence 
\begin{equation}
0 \to \Hh^2(X_*(T)_{\mathcal{I}_K},\EEx)^{\Frob{}} \to \QCiso{\Gr_R(\underline{T})} \to \Hom_\text{qc}(T(K),\EEx) \to 0,
\end{equation}
where $\Hom_\text{qc}(T(K),\EEx)$ denoted the group of quasicharacters of $T(K)$.
We further show that automorphism groups in the $\QC(\Gr_R(\underline{T}))$ are given, for every quasicharacter sheaf $\qcs{F}$ on $\Gr_R(X)$, by
\begin{equation}
\Aut(\qcs{F}) \iso (\check{T}_\ell)^{\Weil{K}}
\end{equation}
where $\Weil{K}$ is the Weil group for $K$ and $\check{T}_\ell$ is the $\ell$-adic dual torus to $T$.
We also use quasicharacter sheaves to categorify the transfer of quasicharacters of tori between characteristic $0$ and characteristic $p$ local fields.

Joseph Bernstein has suggested to us that, although quasicharacter sheaves on $\Gr(\underline{T})$ do not correspond exactly to quasicharacters of $T(K)$, the category $\QC(\Gr_R(\underline{T}))$ is the right one to consider and that $\QC(\Gr(\underline{T})$ may be closely tied to characters of  the pure rational forms of $T$ in the sense of Vogan \cite{vogan:93a} or perhaps the rigid inner twists of Tasho Kaletha. 
A better understanding of 
$\Hh^2(X_*(T)_{\mathcal{I}_K},\EEx)^{\Frob{}}$ should provide insight into this suggestion.

@@

The process of creating a category from the group of quasicharacters of a $p$-adic  torus, as explained above, informs our choice of the term quasicharacter sheaf in this paper.
We also want to situate our terminology in a historical context.
It is not uncommon to refer to local systems satisfying \eqref{introbox} on a connected, commutative algebraic group as character sheaves;
see for example, \cite{kamgarpour:09a}*{Intro}.
As we have indicated, quasicharacter sheaves evolved from this notion,
with an eye toward quasicharacters of $p$-adic groups.
However, the main use of the term character sheaf is of course due to Lusztig.
It is applied to certain perverse sheaves on connected reductive algebraic groups over algebraically closed fields in
\cite{lusztig:85a}*{Def.~2.10} and to certain perverse sheaves on reductive groups
over algebraically closed fields with finite cyclic component groups in the series of papers
beginning with \cite{lusztig:disconnected1}.
When commutative, such groups are extensions of finite cyclic groups by algebraic tori,
in which case it is not difficult to relate Frobenius-stable character sheaves to our quasicharacter sheaves.
The interesting new features that we have found pertaining to Weil sheaves and the non-triviality of $\Hh^2(\pi_0({\bar G}),\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$ do not arise in this context.

@@

%\begin{acknowledgements}
\subsection{Acknowledgments}
We thank Masoud Kamgarpour, Pramod Achar, and Hadi Salmasian
for allowing us to hijack much of our Research in Teams meeting at BIRS into a discussion of
quasicharacter sheaves; their knowledge and help have been invaluable.
We also thank Takashi Suzuki, who made some enormously helpful observations and suggestions.
%
Finally, we gratefully acknowledge the financial support of the Pacific Institute for the Mathematical Sciences
and the National Science and Engineering Research Council,
as well the hospitality of the Banff International Research Station during our week-long stay in May 2012.

@@

\begin{definition}\label{def:QC}
A \emph{quasicharacter sheaf on $G$} is a triple
$\qcs{L}\ceq (\gqcs{L},\mu,\phi)$ where:
\begin{enumerate}
\labitem{(QC.1)}{QC.1} $\gqcs{L}$ is a rank-one $\ell$-adic local system on $\bG$, by which we mean
a constructible $\ell$-adic sheaf on $\bG$, locally constant on each connected
component of $\bG$, whose stalks are one-dimensional $\EE$-vector spaces;
\labitem{(QC.2)}{QC.2} $\mu: \bm^* \gqcs{L} \to \LxL$ is an isomorphism of
sheaves on $\bGxG$ such that the following diagram commutes,
  where $m_3 \ceq m\circ (m\tight{1}{\times}{2}\id) = m\circ (\id\tight{2}{\times}{1} m)$;
  \[
  \begin{tikzcd}[row sep=30]
  \bm_3^*\gqcs{L} \arrow{rr}{(\bm \tight{1}{\times}{2} \id)^*\mu} \arrow[swap]{d}{(\id \tight{2}{\times}{1} \bm)^*\mu}
    &&  \bm^*\gqcs{L} \boxtimes \gqcs{L} \dar{\mu \tight{0}{\boxtimes}{1} \id} \\
    \gqcs{L} \boxtimes \bm^* \gqcs{L} \arrow{rr}{\id \boxtimes \mu}
    &&  \gqcs{L} \tight{0}{\boxtimes}{0} \LxL
  \end{tikzcd}
  \]
\labitem{(QC.3)}{QC.3} $\phi : \Frob{G}^* \gqcs{L} \to \gqcs{L}$ is an
  isomorphism of constructible $\ell$-adic sheaves on $\bG$ compatible with
  $\mu$ in the sense that the following diagram commutes.
  \[
  \begin{tikzcd}[row sep=20]
  \Frob{\GxxG}^* \bm^* \gqcs{L} \arrow{rr}{\Frob{\GxxG}^*\mu}
    && \Frob{\GxxG}^*(\LxL)\\
    \arrow[equal]{u} \bm^*  \Frob{G}^* \gqcs{L} \arrow[swap]{d}{\bm^* \phi}
    && \Frob{G}^*\gqcs{L}\boxtimes \Frob{G}^*\gqcs{L} \dar{\phi\boxtimes \phi} \arrow[equal]{u} \\
    \bm^*\gqcs{L} \arrow{rr}{\mu}
    && \LxL
  \end{tikzcd}
  \]
\end{enumerate}
\end{definition}

@@

\begin{proof}
  Let $\qcs{L}$ be a quasicharacter sheaf on $G$. It is clear \todo{Reference} that
  $\bf^*\gqcs{L}$ is a local system of rank~one, so  \ref{QC.1}  is satisfied.
  To see that $(\bfxf)^* \mu$ satisfies \ref{QC.2},
  apply the functor $(\bfxf)^*$
  to \ref{QC.2} for $\qcs{L}$ and use the canonical isomorphism
  $(\bfxf)^*(\LxL) \iso \bf^*\gqcs{L} \tight{-3}{\boxtimes}{-3} \bf^*\gqcs{L}$.
  To show that $f^*\qcs{L}$ satisfies
  \ref{QC.3}, apply the same functor to \ref{QC.3} for $\qcs{L}$.
  Since $f$ is a morphism of group schemes defined over $\Fq$
  it provides isomorphisms $(\bfxf)^*\Frob{\GxxG}^* \iso \Frob{\GxxG}^* (\bfxf)^*$
  and $(\bfxf)^* \bm^*\iso \bm^* \bf^*$ between functors of constructible sheaves.

@@

Now, let $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$.
Set $\qcs{L}_1 \ceq q_1^* \qcs{L}$ and $\qcs{L}_2 \ceq q_2^* \qcs{L}$;
by Proposition~\ref{prop:pullback}, $\qcs{L}_1$ a quasicharacter sheaf on $G_1$
and $\qcs{L}_2$ is a quasicharacter sheaf on $G_2$.
We will obtain an isomorphism $\qcs{L} \iso  \qcs{L}_1\boxtimes \qcs{L}_2$.
Applying the functor $f^*$ to the isomorphism $\mu$ yields
\begin{equation}\label{eq:fm}
f^*\mu : f^* m^* \gqcs{L} \to f^*(\gqcs{L}\boxtimes \gqcs{L}) .
\end{equation}
We have already observed that $m\circ f = \id_G$, so $f^* m^* \gqcs{L} = \gqcs{L}$.
On the other hand, $f^*(\gqcs{L}\boxtimes \gqcs{L}) = f^*p_1^*\gqcs{L}\otimes f^* p_2^*\gqcs{L}$
by definition.  Since $f^*p_1^*\gqcs{L} = r_1^* q_1^* \gqcs{L}$ and $f^*p_2^*\gqcs{L} = r_2^* q_2^* \gqcs{L}$
we get that $f^*(\gqcs{L}\boxtimes \gqcs{L}) = \gqcs{L}_1\boxtimes \gqcs{L}_2$.
It follows that \eqref{eq:fm} gives an isomorphism $\gqcs{L} \to  \gqcs{L}_1\boxtimes \gqcs{L}_2$.
It is a matter of routine to show that this morphism satisfies
\ref{qc.3} as it applies here,
from which it follows that we have exhibited an isomorphism
$\qcs{L} \to \qcs{L}_1\boxtimes \qcs{L}_2$ of quasicharacters sheaves on $G\times G$.
This completes the proof that $\boxtimes$ is essentially surjective.
\end{proof}

@@

In this section we find a complete characterization of quasicharacter sheaves on étale commutative group schemes over finite fields.

@@

We will see that the Trace of Frobenius may not provide complete
information about isomorphism classes of quasicharacter sheaves on $G$ when $G$ is not a connected algebraic group.
Our main tool for understanding this phenomenon
is a group homomorphism from $\QCiso{G}$ to $\Hh^2(E^\bullet_G)$, defined in Section~\ref{ssec:S}, for which the next two sections are preparation.

>>>>

Motivated by an application to the geometrization and categorification of quasicharacters of $p$-adic tori,
this paper extends Deligne's function--sheaf dictionary for characters of connected commutative algebraic groups over finite fields to characters of smooth commutative group schemes over finite fields.

\subsection{Overview}

@@

In order to extend the dictionary from commutative algebraic groups over finite fields to smooth commutative group schemes $G$ over $\FF_q$ we simply replace the local system $\qcs{E}$ on $G$ with a Weil local system  -- a local system on ${\bar G} := G\times_{\Spec{\FF_q}} \Spec{{\bar \FF}_q}$ -- while retaining the extra structure $\mu_\qcs{E}$. 
Let $\Weil{} \subset \Gal({\bar\FF}_q/\FF_q)$ be the Weil group for $\FF_q$; let $\Frob{G} : \bG \to \bG$ be the Frobenius automorphism for $\bG$.
In this way we are lead to the category $\QC(G)$ of {\it quasicharacter sheaves} on $G$ in which objects are triples $(\gqcs{L}, \mu,\phi)$, where $\gqcs{L}$ is a rank-one local system on ${\bar G}$ and $\phi : \Frob{G}^* \gqcs{L}\to \gqcs{L}$ and $\mu : {\bar m}^* \gqcs{L} \iso \gqcs{L} \boxtimes \gqcs{L}$ are isomorphisms of sheaves; the isomorphisms $\mu$ and $\phi$ must of course be compatible in the obvious way. Morphism in $\QC(G)$ are then homomorphisms of Weil sheaves which are compatible with the extra structure.

We first test the category of quasicharacter sheaves by examining its objects on étale commutative group schemes $G$ over $\FF_q$; étale group schemes form a counterpoint to connected algebraic groups, since the component group of a smooth commutative group scheme is an étale group scheme. 
We find that the group homomorphism 
\begin{equation}
T_G: \QCiso{G} \to \Hom(G(\FF_q),\EEx)
\end{equation}
provided by the trace of Frobenius is surjective with kernel $\Hh^2(\bG,\EEx)^{\Weil{}}$, canonically.
One can show, using the Kunneth formula, that $\Hh^2(\bG,\EEx)$ is non-trivial unless $\bG$ is cyclic.
The fact that $T_G$ is not an isomorphism should not be too troubling because if quasicharacter sheaves $(\gqcs{L}, \mu,\phi)$ and $(\gqcs{L}', \mu',\phi')$ determine the same character of $G(\FF_q)$ then $(\gqcs{L},\phi)$ and $(\gqcs{L}',\phi')$ are isomorphic as Weil sheaves.
Here we also see the importance of working with Weil sheaves; for example, without them, we would not be able to geometrize the character of the étale group scheme $\ZZ$ over $\FF_q$ given by $1\mapsto \ell$, for example.

@@

Having understood quasicharacter sheaves on commutative smooth group schemes over $\FF_q$ in two extreme cases -- connected algebraic groups and étale commutative group schemes -- we turn to the general case. Remarkably, we find that the general case can be understood from these two extreme cases, using the component group sequence
\begin{equation}
0 \to G^0 \to G \to \pi_0(G) \to 0.
\end{equation}
The main result of the paper uses this sequence to find $\QCiso{G}$ by situating it in a canonical short exact sequence
\begin{equation}
0 \to \Hh^2(\pi_0(\bG),\EEx)^{\Weil{}} \to \QCiso{G} \to \Hom(G(\FF_q),\EEx) \to 0.
\end{equation}
We remark that $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$ is non-trivial even for some commutative algebraic groups.
We also illuminate the nature of the category $\QC(G)$ by showing that every morphism in this category is either an isomorphism or trivial, and by showing that 
\begin{equation}
\Aut(\qcs{L}) \iso \Hom(\pi_0(\bG)_{\Weil{}},\EEx),
\end{equation}
canonically, for all quasicharacter sheaves $\qcs{L}$ on $G$.

@@

Specializing to the case when $X_K$ is an algebraic tori $T$ over $K$, and writing $\underline{T}$ for the Neron model $X$ in this case, this paper gives a canonical short exact sequence 
\begin{equation}
0 \to \Hh^2(X_*(T)_{\mathcal{I}_K},\EEx)^{\Weil{}} \to \QCiso{\Gr_R(\underline{T})} \to \Hom_\text{qc}(T(K),\EEx) \to 0,
\end{equation}
where $\Hom_\text{qc}(T(K),\EEx)$ denoted the group of quasicharacters of $T(K)$.
We further show that automorphism groups in the $\QC(\Gr_R(\underline{T}))$ are given, for every quasicharacter sheaf $\qcs{F}$ on $\Gr_R(X)$, by
\begin{equation}
\Aut(\qcs{F}) \iso (\check{T}_\ell)^{\Weil{K}}
\end{equation}
where $\Weil{K}$ is the Weil group for $K$ and $\check{T}_\ell$ is the $\ell$-adic dual torus to $T$.
We also use quasicharacter sheaves to categorify the transfer of quasicharacters of tori between characteristic $0$ and characteristic $p$ local fields.

Joseph Bernstein has suggested to us that, although quasicharacter sheaves on $\Gr(\underline{T})$ do not correspond exactly to quasicharacters of $T(K)$, the category $\QC(\Gr_R(\underline{T}))$ is the right one to consider and that $\QC(\Gr(\underline{T})$ may be closely tied to characters of  the pure rational forms of $T$ in the sense of Vogan \cite{vogan:93a} or perhaps the rigid inner twists of Tasho Kaletha. 
A better understanding of 
$\Hh^2(X_*(T)_{\mathcal{I}_K},\EEx)^{\Weil{}}$ should provide insight into this suggestion.

@@

The process of creating a category from the group of quasicharacters of a $p$-adic  torus, as explained above, informs our choice of the term quasicharacter sheaf in this paper.
We also want to situate our terminology in a historical context.
It is not uncommon to refer to local systems satisfying \eqref{introbox} on a connected, commutative algebraic group as character sheaves;
see for example, \cite{kamgarpour:09a}*{Intro}.
As we have indicated, quasicharacter sheaves evolved from this notion,
with an eye toward quasicharacters of $p$-adic groups.
However, the main use of the term character sheaf is of course due to Lusztig.
It is applied to certain perverse sheaves on connected reductive algebraic groups over algebraically closed fields in
\cite{lusztig:85a}*{Def.~2.10} and to certain perverse sheaves on reductive groups
over algebraically closed fields with finite cyclic component groups in the series of papers
beginning with \cite{lusztig:disconnected1}.
When commutative, such groups are extensions of finite cyclic groups by algebraic tori,
in which case it is not difficult to relate Frobenius-stable character sheaves to our quasicharacter sheaves.
The interesting new features that we have found pertaining to Weil sheaves and the non-triviality of $\Hh^2(\pi_0({\bar G}),\EEx)^{\Weil{}}$ do not arise in this context.

@@

%\begin{acknowledgements}
\subsection{Acknowledgments}
We thank Masoud Kamgarpour, Pramod Achar, and Hadi Salmasian
for allowing us to hijack much of our Research in Teams meeting at BIRS into a discussion of
quasicharacter sheaves; their knowledge and help have been invaluable.
We also thank Takashi Suzuki, who made some very helpful observations and suggestions.
%
Finally, we gratefully acknowledge the financial support of the Pacific Institute for the Mathematical Sciences
and the National Science and Engineering Research Council,
as well the hospitality of the Banff International Research Station during our week-long stay in May 2012.

@@

\begin{definition}\label{def:QC}
A \emph{quasicharacter sheaf on $G$} is a triple
$\qcs{L}\ceq (\gqcs{L},\mu,\phi)$ where:
\begin{enumerate}
\labitem{(QC.1)}{QC.1} $\gqcs{L}$ is a rank-one $\ell$-adic local system on $\bG$, by which we mean a constructible $\ell$-adic sheaf on $\bG$, {\it lisse} on each connected component of $\bG$, whose stalks are one-dimensional $\EE$-vector spaces;
\labitem{(QC.2)}{QC.2} $\mu: \bm^* \gqcs{L} \to \LxL$ is an isomorphism of
sheaves on $\bGxG$ such that the following diagram commutes,
  where $m_3 \ceq m\circ (m\tight{1}{\times}{2}\id) = m\circ (\id\tight{2}{\times}{1} m)$;
  \[
  \begin{tikzcd}[row sep=30]
  \bm_3^*\gqcs{L} \arrow{rr}{(\bm \tight{1}{\times}{2} \id)^*\mu} \arrow[swap]{d}{(\id \tight{2}{\times}{1} \bm)^*\mu}
    &&  \bm^*\gqcs{L} \boxtimes \gqcs{L} \dar{\mu \tight{0}{\boxtimes}{1} \id} \\
    \gqcs{L} \boxtimes \bm^* \gqcs{L} \arrow{rr}{\id \boxtimes \mu}
    &&  \gqcs{L} \tight{0}{\boxtimes}{0} \LxL
  \end{tikzcd}
  \]
\labitem{(QC.3)}{QC.3} $\phi : \Frob{G}^* \gqcs{L} \to \gqcs{L}$ is an
  isomorphism of constructible $\ell$-adic sheaves on $\bG$ compatible with
  $\mu$ in the sense that the following diagram commutes.
  \[
  \begin{tikzcd}[row sep=20]
  \Frob{\GxxG}^* \bm^* \gqcs{L} \arrow{rr}{\Frob{\GxxG}^*\mu}
    && \Frob{\GxxG}^*(\LxL)\\
    \arrow[equal]{u} \bm^*  \Frob{G}^* \gqcs{L} \arrow[swap]{d}{\bm^* \phi}
    && \Frob{G}^*\gqcs{L}\boxtimes \Frob{G}^*\gqcs{L} \dar{\phi\boxtimes \phi} \arrow[equal]{u} \\
    \bm^*\gqcs{L} \arrow{rr}{\mu}
    && \LxL
  \end{tikzcd}
  \]
\end{enumerate}
\end{definition}

@@

\begin{proof}
  Let $\qcs{L}$ be a quasicharacter sheaf on $G$. 
  Pullback by $\bf$ takes rank~one local systems to rank~one local systems.
  To see that $(\bfxf)^* \mu$ satisfies \ref{QC.2},
  apply the functor $(\bfxf)^*$
  to \ref{QC.2} for $\qcs{L}$ and use the canonical isomorphism
  $(\bfxf)^*(\LxL) \iso \bf^*\gqcs{L} \tight{-3}{\boxtimes}{-3} \bf^*\gqcs{L}$.
  To show that $f^*\qcs{L}$ satisfies
  \ref{QC.3}, apply the same functor to \ref{QC.3} for $\qcs{L}$.
  Since $f$ is a morphism of group schemes defined over $\Fq$
  it provides isomorphisms $(\bfxf)^*\Frob{\GxxG}^* \iso \Frob{\GxxG}^* (\bfxf)^*$
  and $(\bfxf)^* \bm^*\iso \bm^* \bf^*$ between functors of constructible sheaves.

@@

Now, let $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$.
Set $\qcs{L}_1 \ceq q_1^* \qcs{L}$ and $\qcs{L}_2 \ceq q_2^* \qcs{L}$;
by Proposition~\ref{prop:pullback}, $\qcs{L}_1$ a quasicharacter sheaf on $G_1$
and $\qcs{L}_2$ is a quasicharacter sheaf on $G_2$.
We will obtain an isomorphism $\qcs{L} \iso  \qcs{L}_1\boxtimes \qcs{L}_2$.
Applying the functor $f^*$ to the isomorphism $\mu$ yields
\begin{equation}\label{eq:fm}
f^*\mu : f^* m^* \gqcs{L} \to f^*(\gqcs{L}\boxtimes \gqcs{L}) .
\end{equation}
We have already observed that $m\circ f = \id_G$, so $f^* m^* \gqcs{L} = \gqcs{L}$.
On the other hand, $f^*(\gqcs{L}\boxtimes \gqcs{L}) = f^*p_1^*\gqcs{L}\otimes f^* p_2^*\gqcs{L}$
by definition.  Since $f^*p_1^*\gqcs{L} = r_1^* q_1^* \gqcs{L}$ and $f^*p_2^*\gqcs{L} = r_2^* q_2^* \gqcs{L}$
we get that $f^*(\gqcs{L}\boxtimes \gqcs{L}) = \gqcs{L}_1\boxtimes \gqcs{L}_2$.
It follows that \eqref{eq:fm} gives an isomorphism $\gqcs{L} \to  \gqcs{L}_1\boxtimes \gqcs{L}_2$.
It is a matter of routine to show that this morphism satisfies
\ref{QC.3} as it applies here,
from which it follows that we have exhibited an isomorphism
$\qcs{L} \to \qcs{L}_1\boxtimes \qcs{L}_2$ of quasicharacters sheaves on $G\times G$.
This completes the proof that $\boxtimes$ is essentially surjective.
\end{proof}

@@

In this section we find a complete characterization of the category of quasicharacter sheaves on étale commutative group schemes over finite fields.

\subsection{Stalks of quasicharacter sheaves}

@@

We will see that $T_G : \QCiso{G} \to G(\Fq)^*$ may not provide complete
information about isomorphism classes of quasicharacter sheaves on $G$ when $G$ is not a connected algebraic group.
Our main tool for understanding this phenomenon
is a group homomorphism $S_G: \QCiso{G} \to \Hh^2(E^\bullet_G)$ defined in Section~\ref{ssec:S}, for which the next two sections are preparation.
